---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dye 
 The package name is dye substance used to impart colour to textiles, paper, leather, and other materials.

<!-- badges: start -->
<!-- badges: end -->

The goal of `dye` is to attach a color palette to a `ggplot` object to modify the default color and fill aesthetics. It can be used with both, categorical/discrete and continuous scales. The package has 5 vibrant colors to match the different types of dyes. 

## Installation

You can install the development version of dye with 

```{r install, eval = FALSE}
devtools::install_github("etc5523-2021/r-package-takehome-pjai0005")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE, message=FALSE}

library(dye)
library(tidyverse)
library(ggplot2)
library(palmerpenguins)

## basic example code

ggplot(penguins, aes(bill_depth_mm, bill_length_mm, color = species)) +
  geom_point( size = 3 ) +
  theme_bw()+
  scale_color_pentagon_d() +
  ggtitle("Example of Discrete Scale (Color)")

ggplot(penguins, aes(bill_depth_mm, bill_length_mm, color = species)) +
  geom_point( size = 3 ) +
  theme_bw()+
  scale_colour_pentagon_d(direction = -1) +
  ggtitle("Example of Discrete Scale (Colour)")

```

## For Fill Aesthetic
```{r, warning=FALSE, message=FALSE}
ggplot(penguins, aes(island, fill = species)) +
  geom_bar() +
  theme_bw()+
  scale_fill_pentagon_d() +
  ggtitle("Example of Discrete Scale (Fill)")

ggplot(penguins, aes(island, fill = species)) +
  geom_bar() +
  theme_bw()+
  scale_fill_pentagon_d(direction = -1)  +
  ggtitle("Example of Discrete Scale (Fill) Reverse Direction")
```
## For Continuous Scales

```{r, warning=FALSE, message=FALSE}

ggplot(penguins, aes(flipper_length_mm, body_mass_g, color = bill_depth_mm)) +
  geom_point( size = 3 ) +
  theme_bw()+
  scale_color_pentagon_seq_c("Indigo Blue") +
  ggtitle("Example of Continuous Scale")


ggplot(penguins, aes(flipper_length_mm, body_mass_g, color = bill_depth_mm)) +
  geom_point( size = 3 ) +
  theme_bw()+
  scale_colour_pentagon_seq_c(direction = -1) +
  ggtitle("Example of Continuous Scale Reverse")

```


